Ch3 process

### 2022-02-18 Ch3_samplesize/Ch3_process.Rmd
The test works and the functions work, so putting these into the actual functions script.

samp.sizes <- c(80, 200, 500, 800, 1000, 1600)
num.ns <- length(samp.sizes)
q.tests <- c(100, 250,500,1000)
num.qs <- length(q.tests)

@@

@@

  ith.a <- mod1$alphas.hat[1]
  ith.k <- mod1$k.hat

  ith.q <- all.qtests[i]
  ith.cdf <- lomax.st(x = ith.q, alpha = ith.a, k = ith.k)
  cdfs.hat[i] <- ith.cdf

@@

>>>>

samp.sizes <- c(80, 200, 500, 800, 1000, 1600)
num.ns <- length(samp.sizes)
q.tests <- c(100, 250,500,750,1000)
num.qs <- length(q.tests)

@@

ith.a <- rep(0, ntests)
ith.k <- rep(0, ntests)

@@

  ith.a[i] <- mod1$alphas.hat[1]
  ith.k[i] <- mod1$k.hat

  ith.q <- all.qtests[i]
  ith.cdf <- lomax.st(x = ith.q, alpha = ith.a[i], k = ith.k[i])
  cdfs.hat[i] <- ith.cdf

@@

lomax.fits <- data.frame(samp.sizes = all.sampsizes, threshold = all.qtests, alphas = ith.a, ks = ith.k, lomax.tail = cdfs.hat,
                         tru.tails = rep(tru.cdfs$w.cdfs, length(samp.sizes)))
```

```{r eval=FALSE, echo=FALSE}
lomax.fits %>% 
  mutate(tails.ratio = lomax.tail/tru.tails,
         thresh = factor(threshold),
         samp.sizes = factor(samp.sizes)) %>%
  mutate(nice.tails = signif(tails.ratio, 3)) %>% 
  ggplot(., aes(x = samp.sizes, y = tails.ratio, color = thresh)) +
  geom_jitter(alpha = 0.8, width = 0.2) +
  labs(title = "Lomax") +
  theme_minimal()
```
